% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%       release v3.0, 16th July 2014
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997, 2014 Cambridge University Press

\documentclass{jfm}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig, subfigure}

% Macros for consistent formatting
\newcommand*{\fig}[1]{Fig.~\ref{#1}}
\newcommand*{\sect}[1]{\S\ref{#1}}
\newcommand*{\eq}[1]{Eqn.~\ref{#1}}

\title{Aeroacoustic Source Mechanisms in High-Speed Jets}

\author{Michael Crawley\aff{1},
  Lior Gefen\aff{2},
  Ching-Wen Kuo\aff{3},
  Mo Samimy\aff{3}\corresp{\email{Samimy.1@osu.edu}}
 \and Roberto Camussi\aff{2}}

\affiliation{\aff{1}Department of Chemical Engineering, University of America,
Somewhere, IN 12345, USA
\aff{2}Department of Aerospace and Mechanical Engineering, University of
Camford, Academic Street, Camford CF3 5QL, UK
\aff{3}Department of Mechanical and Aerospace Engineering, The Ohio State University, Columbus, OH, USA}

\begin{document}

\maketitle

\begin{abstract}
It has been well-known within the aeroacoustic community that the dominant noise sources in high-speed turbulent jets are related to the evolution of the large-scale structures as they convect downstream.
However, the exact dynamics of these large-scale structures which are relevant to the noise generation process are less clear.
This work aims to study the dynamics of, and noise generated by, the large-scale structures in high-fidelity in a Mach 0.9 turbulent jet using plasma-based excitation to produce either individual or periodic coherent ring vortices in the shear layer.
First, two-point cross-correlations are used between the acoustic near-field and far-field in order to identify the dominant noise source region.
The large-scale structure interactions were then investigated by stochastically-estimating the time-resolved velocity fields from time-resolved near-field pressure traces and non-time-resolved planar velocity snapshots using an artificial neural network.
Finally, from Ribner's dilatation-based acoustic analogy the aeroacoustic source terms were computed using the time-resolved velocity field produced by the stochastic estimation.
The results indicated that the disintegration of the coherent ring vortices are the dominant aeroacoustic source mechanism for the jet studied here. 
However, the merging of vortices in the initial shear layer was also identified as a non-trivial noise source mechanism. 
\end{abstract}

\begin{keywords}

\end{keywords}

\include{sect_introduction}
\include{sect_methodology}
\include{sect_nearfield}
\include{sect_velocity_reconstruction}
\include{sect_acoustic_source}
\include{sect_conclusion}

%Acknowledgements should be included at the end of the paper, before the References section or any appendicies, and should be a separate paragraph without a heading. Several anonymous individuals are thanked for contributions to these instructions.

\bibliographystyle{jfm}
\bibliography{master.bib}

\end{document}
